### 2019-06-29 thesis.tex
changes

\section{Kinetic processes in astrophysical plasmas}
\label{sec:astro-plasma}
The plasma, as a collection of ions and electrons, has its dynamics
dominated by the electric and magnetic fields generated by the presence
of charged particles, and electric currents that arise from their
movement. Due to the long-range nature of these self-generated fields,
one particle affects the movement of several other particles, which
will interact with other particles, and so on. This \emph{collective
  behavior}\footnote{A more detailed description on all the processes
  and conditions that characterize the collective behavior in neutral
  plasmas can be seen in Refs. \cite{bitt,gurnett2017,chen}. For
  nonneutral plasmas, see Ref. \cite{DavidsonNonNeutral}.} is what
characterizes an ionized gas as a plasma, and also is the reason behind
the complexity of the plasma dynamics.

% In order to understand what collective processes are, one has to
% have in mind that a plasma is a many-body system composed mostly
% - or completely - of charged particles, that interact with each
% other through electromagnetic forces. Due to the long range nature
% of the electromagnetic forces, one charge can interact with several
% charges at the same time, that will interact with others, and so
% on. In such arrangement, the particle motion, at a certain volume
% element of the plasma, will be affected not only by the surrounding
% environment, but it will also be influenced by the conditions at
% distant regions of the system. This nonlocal characteristic  of the plasma
% dynamics is called \emph{collective behavior} \cite{chen}.

\chapter{Kinetic theory}
\label{sec:kin-theo}
The kinetic theory is the most fundamental description of the
plasma dynamics. Based on the concepts and methods of statistical
mechanics, together with the Maxwell equations, it provides a
formal self-consistent evolution of the plasma processes. This
formalism takes into account the variations of the velocity
distribution function $f({\bf r},{\bf v},t)$ in the phase-space
for each particle species. Statistically, this means that the
product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species
$\alpha$ in a volume element $d^3r$ around ${\bf r}$ and in a
velocity volume element $d^3v$ around ${\bf v}$, at the instant
$t$ \cite{klimo,klimon}.

@@

>>>>

\chapter{Kinetic theory and astrophysical plasmas}
\label{sec:kin-theo}

The plasma is a collection of ions, electrons and neutral particles that has
its dynamics dominated by the electric and magnetic fields, generated by the
electrically charged particles and the electric currents related to their
motion, respectively. Due to the long-range nature of these self-generated
fields, one particle affects the movement of several other particles, which
will interact with other particles, and so on. This \emph{collective behavior}
\footnote{A detailed description of all the processes and conditions that
  characterize the collective behavior in plasmas, can be accessed in the
  following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
is what characterizes an ionized gas as a plasma, and is also the reason
behind the complexity of the plasma dynamics. This complexity comes in the
form of a myriad of self-consistent oscillatory processes, where the electric
and magnetic fields affect - and are affected by - the position and motion of
the charges, and how they vary in time \cite{chen}.

Describing such complicated dynamics it is not an easy task.

The kinetic theory is the most fundamental description of the
plasma dynamics. Based on the concepts and methods of statistical
mechanics, together with the Maxwell equations, it provides a
formal self-consistent evolution of the plasma processes. This
formalism takes into account the variations of the velocity
distribution function $f({\bf r},{\bf v},t)$ in the phase-space
for each particle species. Statistically, this means that the
product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species
$\alpha$ in a volume element $d^3r$ around ${\bf r}$ and in a
velocity volume element $d^3v$ around ${\bf v}$, at the instant
$t$ \cite{klimo,klimon}.

@@

\section{Kinetic processes in astrophysical plasmas}
\label{sec:astro-plasma}
